Replicate earlier study

### 2023-03-31 x_replicate.qmd
nest stab at new study loop

  arp     <- aip |> dplyr::filter(ICAO == .apt,   REF == "ARP")
  rwys    <- aip |> dplyr::filter(ICAO == .apt, ! REF == "ARP")
  apt_box <- airport_centerline_box(rwys, ...)

@@

>>>>

  arp     <- aip |> dplyr::filter(ICAO == .apt,   REF == "ARP")
  rwys    <- aip |> dplyr::filter(ICAO == .apt, ! REF == "ARP")
  rwy_centerline_ls <- cast_rwy_ctr_line_ls(rwys)
  apt_box <- airport_centerline_box(rwys, ...)

@@

part of data cleaning 
- remove stray orphans inside aerodrome

gotcha |> ungroup() |> filter(ARR) |> mutate(GOTCHA = RWY_TRUST >= quantile(RWY_TRUST, probs = 0.1)) |> filter(GOTCHA, N_LAST < 15) |> filter(UID == "3c66b1-1") |> unnest(last_4d) |> ggplot() + geom_point(aes(x = LON, y = LAT)) + geom_point(data = arp, aes(x = LON, y = LAT), color = "red", size = 3) + geom_sf(data = my_apt_box, fill = NA)
